\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-02-24 write_up/mixfishsim_ecolmod.tex
Text update

@@

>>>>

\underline{The why:} \\

Dynamic management requires understanding of the interaction between fishers
and heterogeneously distributed resources. \\

Difficult because of a lack of knowledge of the scale interactions important at
and detailed spatiotemp knowledge. \\

\underline{The what:}  \\

We develop a simulation model to understand scale.\\

Detail of sim model important -- highly resolved, IBM. Make comparison to other
models, e.g. DISPLACE, POSEIDON...\\

Real world spatiotemp closures rarely been able to consider these issues /
designed with these issues fully in mind - NS cod closures, plaice and trevose
box... \\

Use of commercial data increasing - likely to become more important in future.
Also collaborative approach with industry, e.g. hotspot mapping, spatiotemp
advice... \\

\underline{The what it shows:} \\

Our results show commercial data can be useful at right scale and resolution -
depends on scale of process: pop movement etc... Important to consider how
fishers interact / adapt to changes with the resoruce and mgmt. \\

Closure scenarios demonstrate potential tor reduce F - not as high as with real
pop, but good.  Make link to other studies -- read up on these. \\

\underline{The what next:} \\

Other potential uses of the model \\

Survey design \\

commercial index standardization methods \\

Sampling scheme design \\

Testing fleet dynamics models at an aggregated level \\

Bigger picture stuff::  LO, increasing desire for more nuanced spatiotemp
mgmt... Wider applicability: birds, wildlife ??

@@

Study shows ....\\

This is important because .... \\

How we might apply this in future .... \\
